---
title: "An alternative way of running this workshop exercise"
author: "Hector Corrada Bravo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In this document we setup the starting workspace for the workshop to run locally using the `epivizrStandalone` package
and the Rstudio viewer pane, to make it easier to work with.

The goal is to add a genes track for hg19, a track with CpG islands, and a heatmap with expression from the gene expression barcode project.

Let's start the application with hg19 as the reference
for genes track.

```{r, eval=FALSE}
library(epivizrStandalone)
library(Homo.sapiens)

app <- startStandalone(Homo.sapiens, chr="chr11", use_viewer_option=TRUE)
```

Now, let's add the CpG island track included in this package.

```{r, eval=FALSE}
data(cgi_gr)
cgi_track <- app$plot(cgi_gr, datasource_name="CpG Islands")
```

Now, let's add a heatmap with the gene expression barcode data

```{r, eval=FALSE}
data(bcode_eset)
bcode_ms <- app$data_mgr$add_measurements(bcode_eset, "Gene Expression Barcode")
bcode_hmap <- app$chart_mgr$visualize("HeatmapPlot", datasource=bcode_ms)
```


